Item Construction Rules Revisited: Learnings from Measurement of Latent Variables with Gold Standard Items

### 2025-06-17 manuscript.qmd
add descriptive statistics for cognitive interview and pilot samples

@@

First, we constructed items for the physical characteristics of body height, body weight, and age. Age was defined as chronological age or age in years, corresponding to the time elapsed since a person's birth [@montepareYouReOnly1989; @schwallDefiningAgeUsing2012]. Height was defined as the height of an upright person from the sole of the foot to the top of the head in centimeters, and body weight as the physical mass of a person in kilograms [@martinAnthropometrieAnleitungSelbstaendigen1929]. The items were developed by 124 psychology students [deductive item construction, @burischApproachesPersonalityInventory1984] and 24 persons [prototype approach, see @broughtonPrototypeStrategyConstruction1984] who deviate from the German population mean at least one standard deviation in the relevant characteristics (separately for women and men). The 24 persons were asked to think of prototypical behaviors for each construct to assess the whole spectrum of the latent variable. This process produced a total of 138 items (response categories were not tested). In a second step, we examined how these items were interpreted and whether they were connected to ideas unrelated to the constructs using cognitive interviews. We conducted eight interviews with a length of two to three hours and applied various cognitive procedures, including probing, paraphrasing, concurrent-think-aloud, and retrospective-think-aloud [@prueferVerfahrenEvaluationSurvey1996; @prueferKognitiveInterviews2005]. This should be a sufficient number as recommendations suggest five to 30 interviews and indicate that the most serious problems can already be identified with a small number of interviews [@willisCognitiveInterviewing2005]. The interviews were conducted with people from the target group (four women and four men) aged between 21 and 77 (*M* = 44.00, *SD* = 20.80). The level of education ranged from high school diploma to university degree. After the cognitive interviews, misleading items were reformulated or eliminated [@faulbaumWasIstGute2009], resulting in 61 remaining items. In a third step, these 61 items were tested online on a new sample, which initially consisted of 456 people. However, we excluded 66 subjects because they had not completed the questionnaire, resulting in a sample of 390 participants aged between 18 and 77 years (*M* = 32.00, *SD* = 12.80), including 302 women (77.4 %) and 88 men (22.6 %). The level of education was distributed as follows: 0.0 % no school leaving certificate, 3.3 % secondary school leaving certificate/elementary school or equivalent, 17.2 % secondary school or equivalent, 35.9 % vocational baccalaureate or high school diploma, 40.8 % college degree or university degree, 2.8 % doctorate or habilitation. Out of all respondents, 95.4 % stated German as their native language. Based on these survey responses, we excluded items if a) their main item loading was not on the intended factor, b) their main and secondary loadings were almost equal, or c) they had loading below or equal to .30. Additionally, if (d) items had very similar content, items with lower loadings were excluded. Based on these criteria 12 items were selected for each construct (see @tbl-5). For each of the three questionnaires, two versions were created – one with a 6-point scale with verbal endpoints ("does not apply" to "applies", only endpoints were labeled) and fully numerical anchoring for the dichotomous response format with "applies" or "does not apply".

>>>>

dat_interviews <- read.spss("data/Stichprobe kognitive Interviews.sav", 
  to.data.frame = TRUE, use.value.labels = FALSE, na.omit = FALSE)

dat_pilot <- read.spss("data/Pilottest_Studie_3.sav", 
  to.data.frame = TRUE, use.value.labels = FALSE, na.omit = FALSE)

@@

First, we constructed items for the physical characteristics of body height, body weight, and age. Age was defined as chronological age or age in years, corresponding to the time elapsed since a person's birth [@montepareYouReOnly1989; @schwallDefiningAgeUsing2012]. Height was defined as the height of an upright person from the sole of the foot to the top of the head in centimeters, and body weight as the physical mass of a person in kilograms [@martinAnthropometrieAnleitungSelbstaendigen1929]. The items were developed by 124 psychology students [deductive item construction, @burischApproachesPersonalityInventory1984] and 24 persons [prototype approach, see @broughtonPrototypeStrategyConstruction1984] who deviate from the German population mean at least one standard deviation in the relevant characteristics (separately for women and men). The 24 persons were asked to think of prototypical behaviors for each construct to assess the whole spectrum of the latent variable. This process produced a total of 138 items (response categories were not tested). In a second step, we examined how these items were interpreted and whether they were connected to ideas unrelated to the constructs using cognitive interviews. We conducted eight interviews with a length of two to three hours and applied various cognitive procedures, including probing, paraphrasing, concurrent-think-aloud, and retrospective-think-aloud [@prueferVerfahrenEvaluationSurvey1996; @prueferKognitiveInterviews2005]. This should be a sufficient number as recommendations suggest five to 30 interviews and indicate that the most serious problems can already be identified with a small number of interviews [@willisCognitiveInterviewing2005]. The interviews were conducted with `r nrow(dat_interviews)` people from the target group (`r nrow(dat_interviews[dat_interviews$Geschlecht == 1,])` women and `r nrow(dat_interviews[dat_interviews$Geschlecht == 2,])` men) aged between `r min(dat_interviews$Alter)` and `r max(dat_interviews$Alter)` (*M* = `r printnum(mean(dat_interviews$Alter))`, *SD* = `r printnum(sd(dat_interviews$Alter))`). The level of education ranged from high school diploma to university degree. After the cognitive interviews, misleading items were reformulated or eliminated [@faulbaumWasIstGute2009], resulting in 61 remaining items. In a third step, these 61 items were tested online on a new sample, which initially consisted of 456 people. However, we excluded `r 456 - nrow(dat_pilot)` subjects because they had not completed the questionnaire, resulting in a sample of `r nrow(dat_pilot)` participants aged between `r min(dat_pilot$Alter)` and `r max(dat_pilot$Alter)` years (*M* = `r printnum(mean(dat_pilot$Alter))`, *SD* = `r printnum(sd(dat_pilot$Alter))`), including `r nrow(dat_pilot[dat_pilot$Geschlecht == 1,])` women (`r printnum(nrow(dat_pilot[dat_pilot$Geschlecht == 1,]) / nrow(dat_pilot) * 100)` %) and `r nrow(dat_pilot[dat_pilot$Geschlecht == 2,])` men (`r printnum(nrow(dat_pilot[dat_pilot$Geschlecht == 2,]) / nrow(dat_pilot) * 100)` %). The level of education was distributed as follows: `r round(nrow(dat_pilot[dat_pilot$Bildungsniveau == 1,]) / nrow(dat_pilot) * 100, 2)` % no school leaving certificate, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 2,]) / nrow(dat_pilot) * 100)` % secondary school leaving certificate/elementary school or equivalent, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 3,]) / nrow(dat_pilot) * 100)` % secondary school or equivalent, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 4,]) / nrow(dat_pilot) * 100)` % vocational baccalaureate or high school diploma, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 5,]) / nrow(dat_pilot) * 100)` % college degree or university degree, `r printnum(nrow(dat_pilot[dat_pilot$Bildungsniveau == 6,]) / nrow(dat_pilot) * 100)` % doctorate or habilitation. Out of all respondents, `r printnum(nrow(dat_pilot[dat_pilot$Muttersprache == 1,]) / nrow(dat_pilot) * 100)` % stated German as their native language. Based on these survey responses, we excluded items if a) their main item loading was not on the intended factor, b) their main and secondary loadings were almost equal, or c) they had loading below or equal to .30. Additionally, if (d) items had very similar content, items with lower loadings were excluded. Based on these criteria 12 items were selected for each construct (see @tbl-5). For each of the three questionnaires, two versions were created – one with a 6-point scale with verbal endpoints ("does not apply" to "applies", only endpoints were labeled) and fully numerical anchoring for the dichotomous response format with "applies" or "does not apply".
